On the spatial aggregation of ecosystem condition indicators

### 2025-02-20 manuscript/manuscript.qmd
rm pathways 9 and 10

Pathway 9 describe how a single indicators can be aggregated hierarchically from region to region, whereas pathway 10 shows a case were the aggregation process always starts from scratch for each hierarchical spatial level.
As for pathways 7 and 8, pathway 9 and 10 differ in how they propagate the indicator weight (typically area weight) between regions.
SEEA EA describes and prescribes a hierarchical spatial aggregation (pathway 9).
Note that can cause issues with comparability across nested assessment, if one alters the number or size of sub-regions (@sec-comp).

```{r fig-pathways}
#| fig-cap: |
#|   Flowchart showing pathways for the spatial aggregation of variables in ecosystem condition accounting. Normalisation refers to the steps that make a variable conform to the definition of an indicator in SEEA EA, which may include some, but not necesarily all the steps scale, truncate and transform.
#| out-width: 400
#| echo: false
knitr::include_graphics("../img/aggregationPathways.jpg")
```

>>>>

```{r fig-pathways}
#| fig-cap: |
#|   Flowchart showing pathways for the spatial aggregation of variables in ecosystem condition accounting. Normalisation refers to the steps that make a variable conform to the definition of an indicator in SEEA EA, which may include some, but not necesarily all the steps scale, truncate and transform.
#| out-width: 400
#| echo: false
knitr::include_graphics("../img/aggregationPathways.png")
```
